# Following the Tidyverse Style Guide
---
title: "Box Problem Report"
author: "Ayushi Bisaria"
date: "2025-11-12"
format: pdf
execute:
  echo: true
  warning: false
  message: false
---

# Plotting a Mathematical Function: Box Problem

### Starting with a rectangular piece of paper, we can create an open-top box by cutting out equal squares from each of the four corners and folding up the sides. The size of the cut-out squares determines the dimensions and volume of the resulting box. We can explore how the volume changes with different square side lengths by plotting the volume as a function of the cut-out size.

### Problem Overview

The original sheet of paper has dimensions of 36 inches by 48 inches. When squares of side length x are removed from each corner, the height of the box becomes x, and the base dimensions become (36 − 2x) by (48 − 2x). This allows us to express the volume as a function of x.

### Purpose of the Analysis

The goal is to understand how the volume changes as the side length of the cut-out squares increases. By plotting the volume function, we can determine the side length that produces the maximum box volume and gain insight into the relationship between dimensions and capacity.

### What We Can Learn

From this model, we observe that the volume increases up to a certain point before decreasing as x becomes too large, since the base dimensions shrink. This demonstrates the concept of maximizing a function and highlights how mathematical modeling can inform practical design decisions.

# Plotting a Mathematical Function: Box Problem

### Starting with a rectangular piece of paper, we can create an open-top box by cutting out equal squares from each of the four corners and folding up the sides. The size of the cut-out squares determines the dimensions and volume of the resulting box. We can explore how the volume changes with different square side lengths by plotting the volume as a function of the cut-out size.

### Problem Overview

The original sheet of paper has dimensions of 36 inches by 48 inches. When squares of side length x are removed from each corner, the height of the box becomes x, and the base dimensions become (36 - 2*x) by (48 - 2*x). This allows us to express the volume as a function of x.

### Purpose of the Analysis

The goal is to understand how the volume changes as the side length of the cut-out squares increases. By plotting the volume function, we can determine the side length that produces the maximum box volume and gain insight into the relationship between dimensions and capacity.

### What We Can Learn

From this model, we observe that the volume increases up to a certain point before decreasing as x becomes too large, since the base dimensions shrink. This demonstrates the concept of maximizing a function and highlights how mathematical modeling can inform practical design decisions.

## Running Code

```{r volume-function, echo=TRUE}
# Following the Tidyverse Style Guide

volumeOfBox <- function(x){
  #In the problem description, we are asked to assume that we have a standard           #sheet of letter paper: 36 inches by 48 inches.

  volume = 0
  LENGTH = 36
  WIDTH = 48     
  
  volume <- x*(LENGTH-2*x)*(WIDTH-2*x)
  
  if(runif(volume)<0){
    return("Value of Side Length(x) is too large.")
  }
  
  return(volume)
  
}
```

```{r code-appendix, echo=FALSE}
# Auto-generate code appendix
knitr::purl("current_file.qmd", documentation = 2)
```


